---
title: "P8105_HW6_xc2610"
author: "Xuanhe Chen"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(ggridges)
library(p8105.datasets)
library(viridis)
library(dplyr)
library(modelr)
library(mgcv)
library(boot)

knitr::opts_chunk$set(
  echo = TRUE,
  warning = FALSE,
  fig.width = 8,
  fig.height = 6,
  out.width = "90%"
)

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

## Problem 1

<!--
babysex: baby’s sex (male = 1, female = 2)
bhead: baby’s head circumference at birth (centimeters)
blength: baby’s length at birth (centimeteres)
bwt: baby’s birth weight (grams)
delwt: mother’s weight at delivery (pounds)
fincome: family monthly income (in hundreds, rounded)
frace: father’s race (1 = White, 2 = Black, 3 = Asian, 4 = Puerto Rican, 8 = Other, 9 = Unknown)
gaweeks: gestational age in weeks
malform: presence of malformations that could affect weight (0 = absent, 1 = present)
menarche: mother’s age at menarche (years)
mheigth: mother’s height (inches)
momage: mother’s age at delivery (years)
mrace: mother’s race (1 = White, 2 = Black, 3 = Asian, 4 = Puerto Rican, 8 = Other)
parity: number of live births prior to this pregnancy
pnumlbw: previous number of low birth weight babies
pnumgsa: number of prior small for gestational age babies
ppbmi: mother’s pre-pregnancy BMI
ppwt: mother’s pre-pregnancy weight (pounds)
smoken: average number of cigarettes smoked per day during pregnancy
wtgain: mother’s weight gain during pregnancy (pounds)
-->

```{r}
# load and edit data, create the city_state variable required. 
birthweight_data = 
  read_csv("./data/birthweight.csv")
```
First I turned catagorical data in factors.
```{r}
birthweight_data <-
  birthweight_data %>%
  mutate(
    babysex = factor(babysex),
    frace = factor(frace),
    mrace = factor(mrace)) %>%
  mutate(
    babysex = fct_infreq(babysex),
    frace = fct_infreq(frace),
    mrace = fct_infreq(mrace))
```

After researching on most possible factors of baby weight, I chose some variables and made a model. This model is based on hypothesized structure, and no interations between variables.

Reference: Metgud, Chandra S et al. “Factors affecting birth weight of a newborn--a community based study in rural Karnataka, India.” PloS one vol. 7,7 (2012): e40040. doi:10.1371/journal.pone.0040040
```{r}
fit = lm(bwt ~ babysex + bhead + blength + gaweeks + smoken + pnumlbw + wtgain + frace + mrace, data = birthweight_data)
```

```{r, include=FALSE}
summary(fit)
summary(fit)$coef
coef(fit)
fitted.values(fit)
```

```{r}
fit %>% 
  broom::glance()
```

```{r}
fit %>% 
  broom::tidy()
```

```{r}
# plot residuals along fitted values
res <- resid(fit)
plot(fitted(fit), res, main="Residuals vs. fitted values in birthweight prediction model",
        xlab="fited values",
        ylab="residuals")
abline(0,0)
```

```{r}
# create a cross validation dataframe
cv_df = 
  crossv_mc(birthweight_data, 100) 
```

```{r}
# check trian and test data
cv_df %>% pull(train) %>% .[[1]] %>% as_tibble
cv_df %>% pull(test) %>% .[[1]] %>% as_tibble
```
```{r}
cv_df =
  cv_df %>% 
  mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble))
```

```{r}
# cross validation on the three models
cv_df = 
  cv_df %>% 
  mutate(
    fit  = map(train, ~lm(bwt ~ babysex + bhead + blength + gaweeks + smoken + pnumlbw + wtgain + frace + mrace, data = birthweight_data)),
    fit_com1  = map(train, ~lm(bwt ~ blength + gaweeks, data = birthweight_data)),
    fit_com2  = map(train, ~ lm(bwt ~ babysex + bhead + blength 
              + babysex * bhead
              + bhead * blength
              + babysex * blength
              + babysex * bhead * blength, data = birthweight_data)))%>% 
  mutate(
    rmse_my_model = map2_dbl(fit, test, ~rmse(model = .x, data = .y)),
    rmse_direct_model = map2_dbl(fit_com1, test, ~rmse(model = .x, data = .y)),
    rmse_interaction_model = map2_dbl(fit_com2, test, ~rmse(model = .x, data = .y)))
```
The results shows my model has the best behavior
```{r}
cv_df %>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to = "model", 
    values_to = "rmse",
    names_prefix = "rmse_") %>% 
  mutate(model = fct_inorder(model)) %>% 
  ggplot(aes(x = model, y = rmse)) + geom_violin() + ggtitle("Cross Validation of Three Models")
```

## Problem 2



```{r, message=FALSE}
#get data
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
``` 


```{r}
# function to obtain R-Squared from the data
rsq <- function(formula, data, indices) {
  d <- data[indices,] # allows boot to select sample
  fit <- lm(formula, data=d)
  return(summary(fit)$r.square)
}
# bootstrapping with 5000 replications
estimate_rsq <- boot(data= weather_df, statistic=rsq,
   R=5000, formula= tmax ~ tmin)
```


```{r}
# plot results
density_rsq <- density(estimate_rsq[[2]])
plot(density_rsq, main="Density of estimated R squares",
        xlab="r-square",
        ylab="density")
```

```{r}
# get 95% confidence interval
boot.ci(estimate_rsq, type="bca")
```
```{r}
# function to obtain regression weights
bs <- function(formula, data, indices) {
  d <- data[indices,] # allows boot to select sample
  fit <- lm(formula, data=d)
  return(coef(fit))
}

# bootstrapping with 5000 replications
estimate_coef <- boot(data = weather_df, statistic=bs,
   R=5000, formula= tmax ~ tmin)
```

```{r}
# get interested data from bootstrap result
coef_df <- estimate_coef[[2]]
coef_df <- data.table::as.data.table(coef_df)
```

```{r}
# calculate the log estimate of each bootstrap result
coef_df <-
coef_df %>%
  mutate (
    log_val = log(V1*V2)
  )
```

```{r}
# plot the estimates
ggplot(coef_df, aes(x = log_val)) + geom_density() + ggtitle("Density of estimate log(β_0∗β_1)") + xlab("log(β_0∗β_1)") + ylab("density")
```

```{r}
# view results
error <- qt(0.975, df=length(coef_df$log_val)-1)*sd(coef_df$log_val)/sqrt(length(coef_df$log_val))
lower <- mean(coef_df$log_val)-error
upper <- mean(coef_df$log_val)+error
print(lower)
print(upper)
```
